Stochastic Wind Power Forecasting

### 2020-04-18 LaTeX_Code/Paper/paper_1line_Renzo.tex
Added most text from slides to paper.

\setcounter{page}{1}

\begin{document}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production. Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$. We have a total of 363 days to use.}
  \label{fig:data_curtailing}
\end{figure}

@@

\subsection{Physical Constraints}

@@

\subsection{Optimization} \label{opt_sec}
{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}

To initialize the optimization process for the likelihood function of the process $V$, we solve the following least-squares problem which gives us first estimates of the mean reversion parameter $\theta_0$: {\color{red} Add explanation regarding the motivation for this objective function.}

\begin{equation}
\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
\label{inital_theta}
\end{equation}

 where $v_{i,j}=x_{i,j}-p_{i,j}$,  $x_{i,j}$ is historical wind power production and $p_{i,j}$ is the wind power forecast.

 By assuming ergodicity {\color{red} not ergodicity, instead simply for the \textbf{quadratic variation formula}.}, we can obtain a first estimate on the product of the parameters as follows,

\begin{equation}
\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
\end{equation}

Solving for $\alpha$, we have both first estimates and we can also estimate $\delta$ solving the problem

\begin{equation}
\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
\label{likelihood_delta}
\end{equation}

With our estimations of $\bm{\theta}$, we can start the inference processes as follows:
\begin{enumerate}
\item[Step 1.]  initialize;
\item[Step 2.]  optimize the log-likelihood function using  Nelder-Mead optimization algorithm on a mini-batch sampled with replacement;
\item[Step 3.] check if  accuracy threshold is reached. Else, re-initialize the optimization with the most recent result on a larger mini-batch.
\end{enumerate}
%---END SECTION 4---

@@

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{cccc}
\toprule
Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
Provider A  &  $(\add,\add)$      &  \add   & \add    \\
Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}
In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

 \begin{table}[H]
 \centering
 \begin{tabular}{cccc}
 \toprule
 Model & parameters $(\theta_0, \alpha)$  \\
 \midrule
 \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
 \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
 \end{tabular}
 \caption{ \add confidence interval obtained using bootstrap}
 \label{tab:freq_comparison}
 \end{table}
%---END SECTION 6---

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/initial_guess/initial_theta_1.eps}\quad\includegraphics[width=0.42\textwidth]{plots/initial_guess/initial_theta_2.eps}
\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
\end{figure}

\subsection{Negative Log-Lihelihood}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood.eps}\quad\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_refined.eps}
\includegraphics[width=0.6\textwidth]{plots/likelihood/Log-Likelihood_more_refined.eps}
\caption{Negative Log-Likelihood for different domains.}
\label{fig:neg-LL}
\end{figure}

@@

We were able to obtain the following for 
\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
\hline
Formulation   &  parameters $(\theta_0, \alpha,\delta)$    \\ \hline
Without Lamperti transform &   $(1.2,0.1,0.6) \pm (\add , \add) $   \\ \hline
With Lamperti transform &   $(12,0.29) \pm (\add , \add)  $   \\ \hline
\end{tabular}
\caption{We compare the parameters obtained in both the original and Lamperti space. Parameters have been obtained based on \add data points from the Uruguayan pertaining to the year 2019\add .}
\label{tab:model_comparison_2}
\end{table}

@@

\begin{figure}[H]
  \includegraphics[width=56mm,scale=1]{plots/alpha_conv_beta.png}
  \includegraphics[width=56mm,scale=1]{plots/theta_conv_beta.png}
  \caption{We show self-convergence of our algorithm applied to model $2$. We conlcude that the rate  matches that of of Monte Carlo. Data is from Uruguay pertaining to year 2019.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/1.eps}
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/2.eps}\\
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/3.eps}
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/4.eps}
\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Forecast is from Uruguay pertaining to  year 2019.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/1.eps}
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/2.eps}\\
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/3.eps}
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/4.eps}
\caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Actual production plotted in retrospect. Forecast and data is from Uruguay pertaining to  year 2019.}
\end{figure}
%---END SECTION 7---

@@

\begin{Thm}\label{thm:mod2}
Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$. Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
\red{
\begin{equation}\label{Assumption:3}
\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
\end{equation}
}
 Then, $\tau_0=\tau_1=+\infty$ a.s.
\end{Thm}

>>>>

\setcounter{page}{1}
\sloppy
\begin{document}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production. Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$. We have a total of 363 days to use.}
  \label{fig:data_curtailing}
\end{figure}

@@

\subsection{Physical Constraints} \label{Sec: Physical_Constraints}

@@

\subsection{Optimization} \label{opt_sec}

\subsubsection{Initial guess}

To guarantee the good behave for our optimization algorithm, we aim to start the optimization as close as we can from the optimal parameters. We use \textbf{Lease Square Minimization} and \textbf{Quadratic Variation} over the data to find an initial guess, and to tune the hyper-parameter $\epsilon\in(0,\frac{1}{2})$.

\begin{itemize}

\item \textbf{Least Square Minimization:} We consider a set of transitions $\{\Delta V_i\}_{i}$ with $\Delta V_i=V_{i+1}-V_i$ and $\Delta t=t_{i+1}-t_i$. $(V_{i+1}|V_i)$ is a random variable which conditional mean can be approximated by the solution of the system
\begin{equation*}
\begin{cases}
\dif \E\left[V\right]&=-\theta_t\E\left[V\right]\dif t\\
\E\left[V(t_i)\right]&=V_i,
\end{cases}
\end{equation*}
evaluated in $t_{i+1}$ (i.e., $\E\left[V(t_{i+1})\right]$). Then, the random variable $(V_{i+1}-\E\left[V(t_{i+1})\right])$ has approximately zero mean. If we assume that $\theta_t=c\in\R^+$ for all $t\in[t_i,t_{i+1}]$, then $\E\left[V(t_{i+1})\right]=V_ie^{-c\Delta t}$. If we have a total of $n$ transitions, we can write the regression problem for the conditional mean with $L^2$ loss function as
\begin{equation}
c^*\approx\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-\E\left[V(t_{i+1})\right]\right)^2\right]=\arg\min_{c\geq0}\left[\sum_{i=1}^n\left(V_{i+1}-V_ie^{-c\Delta t}\right)^2\right].
\label{Eq-1}
\end{equation}
As Equation (\ref{Eq-1}) is convex in $c$ (composition of convex is convex), it is enough to verify the first order optimality conditions.
\begin{equation*}
\begin{split}
\frac{\partial f}{\partial c}&=\sum_{i=1}^n2(-V_i)(-\Delta t)(V_{i+1}-V_i(1-\theta_0\Delta t))\\
&=\sum_{i=1}^n2V_i\Delta t(V_{i+1}-V_i(1-c\Delta t))\\
&=\sum_{i=1}^n2V_{i+1}V_i\Delta t-2V_i^2\Delta t+2V_i^2\Delta t^2c.
\end{split}
\end{equation*}
Then, $c^{**}$ satisfies
\begin{equation}
c^{**}\approx\frac{\sum_{i=1}^nV_i(V_i-V_{i+1})}{\Delta t\cdot\sum_{i=1}^n(V_i)^2}\quad\text{and}\quad c^*=\max\{c^{**},0\}.
\label{Eq-4}
\end{equation}
Notice that $c^{**}$ has dimension $\mathbf{time}^{-1}$.

\item \textbf{Quadratic Variation:} We approximate the SDE by its E-M scheme. In particular, we approximate the It\^o quadratic variation with the discrete one:
\begin{itemize}

\item It\^o process quadratic variation: $[V]_t=\int_0^t\sigma_s^2\dif s$.
\item Discrete process quadratic variation: $[V]_t=\sum_{0<s\leq t}(\Delta V_s)^2$.

Then, considering $\Delta t$ the time between measurements, we approximate:
\begin{equation}
\theta_0^*\alpha^*\approx\frac{\sum_{i=1}^n(\Delta V_i)^2}{2\Delta t\sum_{i=1}^n(V_i+p_i)(1-V_i-p_i)}.
\label{Eq-2}
\end{equation}

In section (\ref{Sec: Physical_Constraints}) we defined the parameter $\epsilon$ which has as only condition $0<\epsilon<\frac{1}{2}$. Even when it would be reasonable to choose an arbitrary small $\epsilon>0$, we aim to approximate it using the LSM estimator.\\

Fixed $\epsilon$, we call $\mathcal{V}=\{\Delta V_i^\epsilon\}_{i=1}^n$ to the set of $n$ error transitions where for each measurement $X_i$, we have that $V_i=X_i-p_i^\epsilon$. $\mathcal{P}=\{p_i^\epsilon\}_{i=1}^n$ is the corresponding set of forecasts.\\
If we also fix $\theta_0$ and $\alpha$, we can define the set of indexes $\mathbf{I}=\{i\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\theta_0\}$ and $\mathbf{J}=\left\{j\in\{1,\dots,n\}:\text{ the LSM estimation will estimate }\frac{\theta_0\alpha}{\epsilon}\right\}$. From the definition of $\theta_t$, we have that for $\epsilon<<1$, and $p_t=\epsilon$ or $p_t=1-\epsilon$, the approximation $\theta_t\approx\frac{\theta_0\alpha}{\epsilon}$ holds. Then, for $\epsilon$ small enough, $\mathbf{J}$ can be approximated by $$\mathbf{J}\approx\tilde{\mathbf{J}}=\{j\in\{1,\dots,n\}:p_j^\epsilon\in\{\epsilon,1-\epsilon\}\}.$$
Now, coming back to the definition of $\theta_t$, we have that it is more likely that $\theta_t=\theta_0$ if $p_t^\epsilon\approx\frac{1}{2}$. Then, we can approximate $\mathbf{I}$ by $$\mathbf{I}\approx\tilde{\mathbf{I}}=\left\{i\in\{1,\dots,n\}:p_i\in(\gamma,1-\gamma)\right\},\ \gamma\approx\frac{1}{2},\ \gamma<\frac{1}{2}.$$
We do not see signification differences in the LSM estimator for all $\gamma\in(0.1,0.3)$. If $\gamma>0.3$, the reduction in the number of samples makes variations in the LSM estimator. As we have an approximated value for $\theta_0\alpha$, if we can estimate $\frac{\theta_0\alpha}{\epsilon}$, then we can estimate $\epsilon$. We showed that for $\epsilon<<1$, the LSM estimation using indexes from $\tilde{\mathbf{J}}$ is an estimator for $\frac{\theta_0\alpha}{\epsilon}$.

\subsubsection{Negative Log-Likelihood Minimization in $V$ Space} \label{Sec:MinLH}

To find the optimal parameters, we minimize the negative log-likelihood using the derivative-free function \textit{fminsearch} from MATLAB R2019b over the parameters $(\theta_0,\alpha)$. At each step of the iteration,  we:
\begin{itemize}

\item Use the training dataset to find the SDE first and second moments.
\item Match the proxy distribution moments with the SDE moments.
\item Evaluate the negative log-likelihood using the training dataset.

\subsubsection{Negative Log-Likelihood Minimization in $Z$ Space} \label{Sec:MinLHL}

Let $\{\Delta V_i\}_{i=1}^n$ be the set of all error transitions, and $\psi(\theta_0,\alpha,\Delta V)$ the Lamperti transform. Notice that the Lamperti transitions $\{\Delta Z_i\}_{i=1}^n$ depend on $(\theta_0,\alpha)$ because $$\{\Delta Z_i\}_{i=1}^n=\psi(\theta_0,\alpha,\{\Delta V_i\}_{i=1}^n).$$
Then, if we compute $$\max_{(\theta_0,\alpha)}\mathbf{L}(\theta_0,\alpha,\{\Delta Z_i\}_{i=1}^n),$$
we are not computing a MLE in the classical sense, as the data is changing with the parameters. However, we can try to find a fixed point ${\color{blue}(\theta_0^*,\alpha^*)}$ such that
\begin{equation}
{\color{blue}(\theta_0^*,\alpha^*)}=\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{blue}\theta_0^*},{\color{blue}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
\label{FP}
\end{equation}
In this point, the likelihood has a maximum for the data set corresponding to that point.

We are interested in finding the solution of (\ref{FP}). We have that, if $(\theta_0^*,\alpha^*)$ is a solution of (\ref{FP}), then
\begin{equation*}
(\theta_0^*,\alpha^*)-\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right)=0.
\end{equation*}
Given a pair $(\theta_0^{*},\alpha^{*})$, we call $(\theta_0^{**},\alpha^{**})$ to the solution of
\begin{equation*}
\arg\max_{(\theta_0,\alpha)}\mathbf{L}\left(\theta_0,\alpha,\psi({\color{black}\theta_0^*},{\color{black}\alpha^*},\{\Delta V_i\}_{i=1}^n)\right).
\end{equation*}
For each $(\theta_0^{*},\alpha^{*})$, we define the relative error function
\begin{equation*}
\Psi(\theta_0^{*},\alpha^{*})=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|}
\end{equation*}
and claim that $(\theta_0^*,\alpha^*)$ is a fixed point iff $\Psi(\theta_0^*,\alpha^*)=0$.

\subsubsection{Additional Parameter $\delta$}

{\color{red}[I am not sure if we should introduce this parameter here, of in some previous section].} We observe that for each day, the error at time $t=0$ is not zero. However, by construction of the forecast, we may assume that for some time in the past $t_\delta<0$, the error $V_{t_\delta}=0$.\\
\quad\\
We extrapolate linearly $p(t)$ considering the truncation at $\epsilon$, so we can evaluate $p(t_{-\delta})$, and assume that $V(t_{-\delta})=0$. Then, for each day $j$, we have an initial transition $(V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta)$. We assume again that it is Beta and apply the same moment matching as for the rest of transitions. With our initial guess for $\bm{\theta}$, we can construct our initial guess for $\delta$ solving the problem

\begin{equation*}
\delta\approx\arg\min_{\delta}\mathcal{L}_{\delta}(\bm{\theta},\delta; V^{M,1}) = \arg\min_{\delta}\prod\limits_{j=1}^M \rho_0 (V_{j, t_0}|V_{j, t_{-\delta}};\bm{\theta},\delta) \,.
\label{likelihood_delta}
\end{equation*}
To solve this minimization problem, we repeat the steps described in section (\ref{Sec:MinLH}), with the additional initial step of creating the linear extrapolation.

%---END SECTION 4---

@@

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
Forecast Provider & Parameters $(\theta_0, \alpha,\delta)$ & Product $\theta_0\alpha$ \\ \midrule
Provider A  &  $(\add,\add)$      &  \add    \\
Provider B  & $(\add,\add) $  &  \add \\ 
Provider C  & $(\add,\add) $  &  \add \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}
In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

%---END SECTION 6---

@@

\subsection{Negative Log-Likelihood in $V$ Space}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/normal/Log-Likelihood.jpg}
\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
\label{fig:neg-LL}
\end{figure}
On Figure (\ref{fig:neg-LL}), we can see the level sets for the negative log-likelihood. The thick violet band is the region where the function reaches its minimums.\\
We can see the \textbf{initial guess} point, the result of three different \textbf{optimization tools} from MATLAB, and the minimum point that we found from the \textbf{evaluations} that generate the plot.
\begin{table}[]
\centering
\begin{tabular}{lccc}
\toprule
 & $\theta_0$ & $\alpha$ & $\theta_0\alpha$\\
 \midrule
 Initial guess & 1.629 & 0.060 & 0.098 \\
 fminsearch & 1.135 & 0.073 & 0.083 \\
 fmincon & 1.366 & 0.061 & 0.083 \\
 fminunc & 1.628 & 0.051 & 0.083 \\
 evaluations & 1.180 & 0.070 & 0.083 \\
 \bottomrule
\end{tabular}
\end{table}

\subsection{Negative Log-Likelihood in $Z$ Space}

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
\caption{Negative Log-Likelihood {\color{red}[Low quality picture]}.}
\label{fig:neg-LLL}
\end{figure}
In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets of the error function $\Psi$.\\
The center deep green band is the set $\mathbb{A}$ such that $\Psi(\mathbb{A})\in[0.05,0.1]$. We do not achieve relative error smaller than 0.05.\\
We observe a particular behavior over the curves $\theta_0\alpha=k\in\R^+$. However, it can be a numeric effect.\\
We also observe that: $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.083\}\neq\emptyset.$$
On the right, we observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.038$ from the error SDE.\\
We choose $(\theta_0,\alpha)=(2.200,0.038)$.\\
We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".

@@

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Forecast is from Uruguay pertaining to  year 2019.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
\caption{We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Actual production plotted in retrospect. Forecast and data is from Uruguay pertaining to  year 2019.}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
\end{figure}

We can see two histograms for the error transitions. On the left, using $(\theta_0^E,\alpha^E)$, while on the right, using $(\theta_0^L,\alpha^L)$.

%---END SECTION 7---

@@

\begin{Thm}\label{thm:mod2}
Assume that assumptions of Theorem \ref{thm:exun} hold with $x_0\in]0,1[$.
Let $\tau_0:=\inf \{t\in[0,T],\; X_t=0\}$ and  $\tau_1:=\inf \{t\in[0,T],\; X_t=1\}$ with the convention that $\inf\emptyset=+\infty$. Assume in addition that for all $t\in[0,T]$,  $p_t\in]0,1[$ and that
\red{
\begin{equation}
\theta_t\geq \max\left(\frac{\alpha\theta_0+\dot p_t}{1-p_t},\frac{\alpha\theta_0-\dot p_t}{p_t}\right)\tag{C}. 
\end{equation}
}
 Then, $\tau_0=\tau_1=+\infty$ a.s.
\end{Thm}
